Prediction maps of defoliation at trees

### 2019-05-24 analysis/report-defoliation.Rmd
wflow_publish("analysis/report-defoliation.Rmd")

---
title: "Prediction maps of defoliation at trees"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
author: "Patrick Schratz, Marc Becker, Friedrich-Schiller-University Jena"
---

>>>>

---
title: "Prediction maps of defoliation at trees"
output: 
  workflowr::wflow_html:
    includes:
      in_header: header.html
editor_options:
  chunk_output_type: console
author: "Patrick Schratz, Marc Becker, Friedrich-Schiller-University Jena"
---
